Kernel k-Groups via Hartigan's Method

### 2018-08-10 energy_clustering/pami18/energy_clustering.tex
added jovo bio

\begin{IEEEbiographynophoto}{Joshua Vogelstein}
Biography text here.
\end{IEEEbiographynophoto}

>>>>

\begin{IEEEbiographynophoto}{Joshua T.~Vogelstein}
I received a B.S degree from the Department of Biomedical Engineering (BME) at Washington University in St. Louis, MO in 2002, a M.S. degree from the Department of Applied Mathematics and Statistics (AMS) at Johns Hopkins University (JHU) in Baltimore, MD in 2009, and a Ph.D. degree from the Department of Neuroscience at JHU in 2009. I was a Postdoctoral Fellow in AMS@JHU from 2009 until 2011, at which time I was appointed an Assistant Research Scientist, and became a member of the Institute for Data Intensive Science and Engineering. I spent 2 years at Information Initiative at Duke University, before coming home to my current appointment as Assistant Professor in BME@JHU, and core faculty in both the Institute for Computational Medicine and the Center for Imaging Science, as well as a member of the Kavli Neuroscience Discovery Institute. I married my kindergarten sweetheart in the summer of 2014.

My primary research interest is to extend and fuse statistical machine learning and big data science to address the most important brain science and mental health questions of our time, particularly  connectomics. Our group’s research has been featured in a number of prominent scientific and engineering journals and conferences including Nature, Nature Methods, Science, Cell, PNAS, Science Translational Medicine, JMLR, PAMI, Annals of Applied Statistics,  NIPS, and SIAM Journal of Matrix Analysis and Applications. In 2011, I co-founded the Open Connectome Project which expanded in 2015 to be NeuroData, whose mission is to enable terascale neuroscience for everyone. All our work is conducted according to the highest standards of open science.
\end{IEEEbiographynophoto}
